\Large Clustering Trips Identified from Automatic Number \\ Plate Recognition Camera Scans

### 2018-02-01 discussion.tex
Fixed some grammar mistakes and added abstract
All sections now covered.

Most urban cities in the world possess a network of ANPR cameras that is used in law enforcement and for traffic monitoring and control. Number plate data collected in the Tyne and Wear area is stored and leveraged by the UTMC for computing average journey times across a selection of sensitive roads. However, number plate data could be used more extensively to identify and study individual and collective travel patterns. In this paper, we've presented a set of definitions and constraints that establish a conceptual foundation for identifying vehicle trips from number plate detections. We've identified two parameters, $\tau$ and $\Tau$ as critical in the discrimination of plausible and unplausible trips. Hence, future work should first and foremost focus on developing formal methods to estimate these parameters from observed distributions of travel times and by applying knowledge about the structure of the road network. Moreover, methods for addressing issues concerning camera performance, namely wrong and duplicate scans, should be further developed and researched.

Once trip data has been computed, a range of interesting applications is available. This work tries to identify groups of vehicles by clustering information about frequency and diversity of travel. By associating a vehicle with a cluster that represents taxis, or home-to-work commuters, one can begin estimating trip mode usage across the city. However, the results presented here could benefit from extra work and further validation. Finally, future work can focus on using trip data to solve interesting research problems such as: 
\begin{enumerate*}[label=(\roman*)]
  \item real-time route recommendation using probabilistic graphical models;
  \item detection of abnormal trip patterns for helping law enforcement in the identification of suspect vehicles or behavior;
  \item modelling how drivers make routing choices in the presence of anomalies in the road network.
\end{enumerate*}

>>>>

Most urban cities in the world possess a network of ANPR cameras that are used for law enforcement as well as traffic monitoring and control. Number plate data collected in the Tyne and Wear area is stored and leveraged by the UTMC for computing average journey times across a selection of sensitive roads. However, number plate data could be used more extensively to identify and study individual and collective travel patterns. In this paper, we have presented a set of definitions and constraints that establish a conceptual foundation for identifying vehicle trips from number plate detections. We also identify two parameters, $\tau$ and $\Tau$ as critical in the discrimination of plausible and implausible trips. Hence, future work should first and foremost focus on developing formal methods to estimate these parameters from observed distributions of travel times and by applying knowledge about the structure of the road network. Moreover, methods for addressing issues concerning camera performance, namely wrong and duplicate scans, should be further developed and researched.

Once trip data has been computed, a range of interesting applications are available. This work tries to identify groups of vehicles by clustering information about frequency and diversity of travel. By associating a vehicle with a cluster that represents taxis, or home-to-work commuters, one can begin estimating trip mode usage across the city. However, the results presented here could benefit from extra work and further validation. Finally, future work can focus on using trip data to solve interesting research problems such as:
\begin{enumerate*}[label=(\roman*)]
  \item real-time route recommendation using probabilistic graphical models;
  \item detection of abnormal trip patterns for helping law enforcement in the identification of suspect vehicles or behaviour;
  \item modelling how drivers make routing choices in the presence of anomalies in the road network.
\end{enumerate*}

### 2018-02-01 paper.tex
Used bits from other sections as the related work. Had to move figure 1 around so that the structure of the paper would not be affected as a result.
All sections now covered.

\begin{abstract} \small\baselineskip=9pt In major cities, government agencies increasingly employ automatic number plate recognition (ANPR) technology in law enforcement and traffic control. In the region of Tyne and Wear (UK) the network of ANPR cameras is used to monitor travel times across sensitive roads. However, few works have explored the full potential of number plate scans for analysing individual and collective travel patterns. In this work we present a methodology for deriving trips from vehicle sightings at fixed camera locations. We illustrate the effect of parameters $\tau$ and $\Tau$ on trip discrimination and on the detection of implausible trips. To demonstrate the potential of trip data we apply \emph{k-means} clustering to trips identified from over 40 million plate scans recorded over 15 weekdays. Results show that whilst private and transit travel modes can begin to be inferred from the resulting clusters, further work needs to be put into developing a more consistent and integrated framework for trip identification in ANPR data.\end{abstract}

>>>>

\begin{abstract} \small\baselineskip=9pt In major cities, government agencies increasingly employ automatic number-plate recognition (ANPR) technology in law enforcement and traffic control. In the Tyne and Wear region (UK) the network of ANPR cameras is used to monitor travel times across sensitive roads. However, few works have explored the full potential of number-plate scans for analysing individual and collective travel patterns. In this work we present a methodology for deriving trips from vehicle sightings at fixed camera locations. We illustrate the effect of parameters $\tau$ and $\Tau$ on trip discrimination and on the detection of implausible trips. To demonstrate the potential of trip data we apply \emph{k-means} clustering to trips identified from over 40 million plate scans recorded over fifteen weekdays. Results show that whilst private and transit travel modes can begin to be inferred from the resulting clusters, further work needs to be put into developing a more consistent and integrated framework for trip identification in ANPR data.\end{abstract}
